Lyman-$\alpha$ photons through rotating outflows

### 2018-03-28 paper/paper.tex
adding bimodality plots

In order to compare the line created with the radiative transfer (RT) process that
involves the rotation and the line with only outflows that is Doppler
shifted (DS), we calculate three main characteristics for each spectrum. We
measure the line's mean velocity, standard deviation and skewness for both
RT's and DS's approaches. We plot the results for each value in Figures
\ref{fig:mean_line}, \ref{fig:standard_deviation} and \ref{fig:skewness},
respectively for $\tauh = 10^7$. We highlight that these 3 plots increase
their fit tendency with a higher optical depth. The reasons why will be
discussed in section \ref{sec:discussion}.

\begin{figure*}
\begin{center}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau7.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau7.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau7.pdf}
\end{center}
\caption{\textbf{Standard Deviation for RT and DS:} The triangles represent the Radiative
  Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
  \label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
  \end{center}
  \caption{\textbf{Skewness for RT and DS:} The triangles represent the Radiative
    Transfer and the lines represent the Doppler Shift. We fixed $\tauh=10^7$.
    \label{fig:skewness}}
\end{figure*}

@@

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure*}
\begin{center}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the
		higher the valley intensity. We fixed $\vout=5$\kms and $\vrot=100$\kms.
		\label{fig:valley_intensity}}
\end{figure*}

>>>>

In order to compare the line created with the radiative transfer (RT) process that
involves the rotation and the line with only outflows that is Doppler
shifted (DS), we calculate three main characteristics for each spectrum. We
measure the line's standard deviation (STD), skewness (SKW) and bimodality (BI) 
for both RT's and DS's approaches. We use the definitions in Eqs. \ref{eq:std}, 
\ref{eq:skw}, \ref{eq:bi} for each value \citep{kokoska1999}.

\begin{equation}
\label{eq:std}
\mathrm{STD} = \sqrt{m_2},
\end{equation}

\begin{equation}
\label{eq:skw}
\mathrm{SKW} = \frac{m_3}{m_2^{3/2}},
\end{equation}

\begin{equation}
\label{eq:bi}
\mathrm{BI} = \mathrm{KURTOSIS} - \mathrm{SKW}^2 = \frac{m_4}{m_2^{2}} - \frac{m_3^2}{m_2^{3}},
\end{equation}

where each $m_i$ is the i-th moment about the mean. The STD has velocity units and 
quantifies the dispersion of the line's velocity: the larger it is, the wider the line. 
The SKW is adimensional and quantifies the peaks' asymmetry: if it is $>0$ the left peak is 
taller and if it is $<0$ the right peak is taller. The BI has velocity$^{-1}$ units and
quantifies if the line has 1 or 2 peaks: it is always $\geq 1$ and the closer it is to 1 the more
bimodal is the line (i.e. has 2 peaks).

We plot the results for each 
value in Figures \ref{fig:standard_deviation}, \ref{fig:skewness} and \ref{fig:bimodality},
respectively for $\tauh = 10^7$. We highlight that these 3 plots increase their fit 
tendency with a higher optical depth. The reasons why will be discussed in section 
\ref{sec:discussion}.

\begin{figure*}
\begin{center}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau5.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau6.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout5_logtau7.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout25_logtau7.pdf}
\includegraphics[height=0.3\textwidth]{./figures/results/line_characterization_std_vout50_logtau7.pdf}
\end{center}
\caption{\textbf{Standard Deviation for RT and DS:} The triangles represent the Radiative
  Transfer and the lines represent the Doppler Shift.
  \label{fig:standard_deviation}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout5_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout25_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_skw_vout50_logtau7}
\end{center}
\caption{\textbf{Skewness for RT and DS:} The triangles represent the Radiative
    Transfer and the lines represent the Doppler Shift.
    \label{fig:skewness}}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout5_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout25_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout50_logtau5}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout5_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout25_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout50_logtau6}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout5_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout25_logtau7}
\includegraphics[height=0.31\textwidth]{./figures/results/line_characterization_bi_vout50_logtau7}
\end{center}
\caption{\textbf{Bimodality for RT and DS:} The triangles represent the Radiative
	Transfer and the lines represent the Doppler Shift.
	\label{fig:bimodality}}
\end{figure*}

@@

% Esta figura deberia tener en el eje x theta y en el eje y intensity of valley
% cada panel tiene una curva para logtau = 5, 6, 7.
\begin{figure*}
\begin{center}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau5}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau5}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau5}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau6}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau6}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau6}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout5_vrot100_logtau7}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout25_vrot100_logtau7}
\includegraphics[height=0.29\textwidth]{./figures/results/line_characterization_vi_vout50_vrot100_logtau7}
\end{center}
\caption{\textbf{Valley Intensity:} We show for each \tauh the dependency that
		the viewing angle $\theta$ has on the line's the valley intensity. The larger
		$\cos{\theta}$ the lower is the valley intensity, so the higher $\theta$, the
		higher the valley intensity. Also, the higher \tauh, the better is the fit RT-DS.
		We fixed $\vrot=100$\kms.
		\label{fig:valley_intensity}}
\end{figure*}
